Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-16 paper/paper.tex
write more on scattering

Let $\boldsymbol{\psi} \in \mathbf{L}^2(\mathbb{R}, \mathbb{C})$ a Hilbert-analytic filter with null average, unit dimensionless center frequency, and an equivalent rectangular bandwidth (ERB) equal to $1/Q$.
We define a constant-$Q$ wavelet filterbank as the family $\boldsymbol{\psi}_{\lambda} : t \mapsto \lambda \boldsymbol{\psi}(\lambda t)$.
Each wavelet $\boldsymbol{\psi}_{\lambda}$ has a center frequency of $\lambda$, an ERB of $\lambda/Q$, and an effective receptive field of $(2\pi Q/\lambda)$ in the time domain.
In practice, we define $\boldsymbol{\psi}$ as a Morlet wavelet:
\begin{equation}
\boldsymbol{\psi}:t \longmapsto \exp\left(-\dfrac{t^2}{2\sigma_{\psi}^2}\right) 
\big[ \exp\left(2\pi \mathrm{i}t\right) - \kappa_{\psi} \big],
\end{equation}
where the Gaussian width $\sigma_{\psi}$ grows in proportion with the quality factor $Q$ and the corrective term $\kappa_{\psi}$ ensures that $\boldsymbol{\psi}$ has a null average over $\mathbb{R}$.
Moreover, we discretize the frequency variable $\lambda$ according to a geometric progression of common ratio $2^{\frac{1}{Q}}$.

We set the constant quality factor of the wavelet filterbank $(\boldsymbol{\psi}_\lambda)_\lambda$ to $Q=12$, thus matching twelve-tone equal temperament in music.
Convolving the wavelets in this filterbank with an input waveform $\boldsymbol{x}\in\mathbf{L}^2(\mathbb{R}$, followed by an application of the pointwise complex modulus, yields the wavelet scalogram
\begin{equation}
\mathbf{U_1}\boldsymbol{x}(t,\lambda) =
\big\vert
\boldsymbol{x}
\ast
\boldsymbol{\psi}_{\lambda}
\big\vert(t)
=
\left\vert
\int_{\mathbb{R}}
\boldsymbol{x}(t^{\prime})
\,
\boldsymbol{\psi}_{\lambda} (t - t^{\prime})
\;
\mathrm{d}{t^\prime}
\right\vert,
\end{equation}
indexed by time $t$ and frequency $\lambda$.

\begin{equation}
\Psi : (t,\log_2 \lambda) \longmapsto 
\exp\left(-\dfrac{t^2+(\log_2 \lambda)^2}{2\sigma^2}\right) 
\Big[ \exp\big(2\pi \mathrm{i} (t + \log_2 \lambda)\big) - \kappa \Big]
\end{equation}

\ml{VL. provide parameters for scattering
\texttt{
case 'tfscat'
    tm\_filt\_opt.Q = [12 1];
    tm\_filt\_opt.J = T\_to\_J(sr*setting.sct/1000, tm\_filt\_opt);
    fr\_filt\_opt.J = 4;}}

>>>>

Let $\boldsymbol{\psi} \in \mathbf{L}^2(\mathbb{R}, \mathbb{C})$ a Hilbert-analytic filter with null average, unit dimensionless center frequency, and an equivalent rectangular bandwidth (ERB) equal to $1/Q$.
We define a constant-$Q$ wavelet filterbank as the family $\boldsymbol{\psi}_{\lambda} : t \mapsto \lambda \boldsymbol{\psi}(\lambda t)$.
Each wavelet $\boldsymbol{\psi}_{\lambda}$ has a center frequency of $\lambda$, an ERB of $\lambda/Q$, and an effective receptive field of $(2\pi Q/\lambda)$ in the time domain.
In practice, we define $\boldsymbol{\psi}$ as a Morlet wavelet:
\begin{equation}
\boldsymbol{\psi}:t \longmapsto \exp\left(-\dfrac{t^2}{2\sigma_{\psi}^2}\right) 
\big[ \exp\left(2\pi \mathrm{i}t\right) - \kappa_{\psi} \big],
\label{eq:psi}
\end{equation}
where the Gaussian width $\sigma_{\psi}$ grows in proportion with the quality factor $Q$ and the corrective term $\kappa_{\psi}$ ensures that $\boldsymbol{\psi}$ has a null average over $\mathbb{R}$.
Moreover, we discretize the frequency variable $\lambda$ according to a geometric progression of common ratio $2^{\frac{1}{Q}}$.
Thus, the base-two logarithm of center frequency, denoted by $\log_2 \lambda$, follows an arithmetic progression.
We set the constant quality factor of the wavelet filterbank $(\boldsymbol{\psi}_\lambda)_\lambda$ to $Q=12$, thus matching twelve-tone equal temperament in music.

Convolving the wavelets in this filterbank with an input waveform $\boldsymbol{x}\in\mathbf{L}^2(\mathbb{R}$, followed by an application of the pointwise complex modulus, yields the wavelet scalogram
\begin{equation}
\mathbf{U_1}\boldsymbol{x}(t,\log_2\lambda) =
\big\vert
\boldsymbol{x}
\ast
\boldsymbol{\psi}_{\lambda}
\big\vert(t)
=
\left\vert
\int_{\mathbb{R}}
\boldsymbol{x}(t^{\prime})
\,
\boldsymbol{\psi}_{\lambda} (t - t^{\prime})
\;
\mathrm{d}{t^\prime}
\right\vert,
\end{equation}
indexed by time $t$ and log-frequency $\log_2\lambda$.
Then, we define a two-dimensional Morlet wavelet $\boldsymbol{\Psi}$, taking a spectrotemporal pair $(t, \log_2 \lambda)$ as input:
\begin{equation}
\Psi : (t,\log_2 \lambda) \longmapsto 
\exp\left(-\dfrac{t^2+(\log_2 \lambda)^2}{2\sigma_{\Psi}^2}\right) 
\Big[ \exp\big(2\pi \mathrm{i} (t + \log_2 \lambda)\big) - \kappa_{\Psi} \Big].
\end{equation}
In the equation above, the Gaussian width $\sigma_{\Psi}$ is chosen so that the quality factor of the Morlet wavelet $\Psi$ is equal to $1$, both over the time dimension and over the log-frequency dimension.
Furthermore, the corrective term $\kappa_{\Psi}$ ensures that $\boldsymbol{\Psi}$ has a null average over $\mathbb{R}^2$, similarly to Equation \ref{eq:psi}.
